### 2012-05-09 Rctl/inst/doc/manual.Rnw
[Rctl] More working on the manual

\textbf{\sffamily Abstract}: Introduction into quanitative correlation locus (CTL) mapping using 
the R package 'ctl'
\vfill

@@

\textbf{\sffamily Introduction}
Some introduction text

@@

\emph{Loading your Excel / CSV data}
Use the example excel file and simply replace the example data by your own then: 
  $$File->Save As->TODO$$

@@

<<echo=TRUE,eval=FALSE>>=
setwd("<PATH_TO_DATA>")
genotypes <- read.csv("genotypes.csv",row.names=1,col.names=TRUE)
phenotypes <- read.csv("phenotypes.csv",row.names=1,col.names=TRUE)
ctls <- CTLscan(genotypes, phenotypes)
@

\emph{Use an R/qtl formatted dataset}
Provided is the main interface functions to R/qtl: $CTLscan.cross()$ this functions accepts and 
R/qtl formatted cross object as input and will scan CTL, perform permutations and transform the
detected differential correlation to LOD score matrices.
As an example we show the code to scan the multitrait dataset provided in R/qtl:

>>>>

\textbf{\sffamily Abstract}: Correlated Trait Loci (CTL) mapping using the R package 'ctl'
\vfill

@@

\textbf{\sffamily Some words in advance}
\nopagebreak

Welcome reader to this tutorial, you'll be thrown into the world of network reconstruction 
using differential correlations. This methodology CTL mapping is not the easiest but the 
results can be of great help unraveling trait to trait interactions in all types of 
eukaryotes. In this tutorial I'll try to use as few difficult concepts as possible. But
some always $sneak$ in.\\
\\
Enjoy this tutorial, and good luck hunting that heritability.\\
Danny Arends\\
\\
PS. Use a text-editor\\
PPS. Use a repository/backup system

\textbf{\sffamily Background \& Methodology}
\nopagebreak

Some introduction on the methodology, skip this chapter first (Do come back later) if you 
have a dataset and just want to use the software.

@@

\emph{Loading your Excel / CSV data}\\
Use the example excel file and simply replace the example data by your own then: 
  $$File->Save As->TODO$$

@@

<<echo=TRUE,eval=FALSE>>=
setwd("<PATH_TO_DATA>")
genotypes <- read.csv("genotypes.csv",row.names=1,col.names=TRUE)
traits <- read.csv("traits.csv",row.names=1,col.names=TRUE)
genotypes[1:5,1:10] #Show the first 5 individuals, 10 markers
traits[1:5,1:10] #Show the first 5 individuals, 10 traits
@

\emph{Use an R/qtl formatted dataset}\\
Provided is the main interface functions to R/qtl: $CTLscan.cross()$ this functions accepts and 
R/qtl formatted cross object as input and will scan CTL, perform permutations and transform the
detected differential correlation to LOD score matrices.
As an example we show the code to scan the multitrait dataset provided in R/qtl:
